---
title: "RWorksheet#5_group(1&9)."
author: "GROUP 1&9 BSIT-2B"
date: "2023-11-30"
output: pdf_document
---

```{r}
library(rvest)
library(httr)
library(dplyr) 
library(polite)
library(kableExtra)
```

##Extracting TV Shows Reviews

1. Each group needs to extract the top 50 tv shows in Imdb.com. It will include the rank, the title of the
tv show, tv rating, the number of people who voted, the number of episodes, the year it was released.

```{r}

polite::use_manners(save_as = 'polite_scrape.R')

url <- 'https://m.imdb.com/chart/toptv/?ref_=nv_tvv_250'

session <- bow(url, user_agent = "Educational")
session

title_show <- character(0)
list_year_ep <-character(0)
 
title_show <- scrape(session) %>%
  html_nodes('h3.ipc-title__text') %>% 
  html_text
 
title_show_only <- as.data.frame(title_show[2:51])
title_show_only
colnames(title_show_only) <- "Rank"

show_df <- strsplit(as.character(title_show_only$Rank),".",fixed = TRUE)
show_df <- data.frame(do.call(rbind,show_df))

show_df <- show_df[-c(3:4)] 

#renaming column 1 and 2
colnames(show_df) <- c("Rank","Title") 
show_df
 

list_year_ep <- scrape(session) %>%
  html_nodes('span.sc-479faa3c-8.bNrEFi.cli-title-metadata-item
') %>% 
  html_text

 
years_only <- c()
for (i in seq(1, length(list_year_ep), by = 3)) {
  years_only <- c(years_only, list_year_ep[i])
}
Year <- years_only[1:50]
Year

ep_only <- c()
for (i in seq(2, length(list_year_ep), by = 3)) {
  ep_only <- c(ep_only, list_year_ep[i])
}
Episode <- ep_only[1:50]
Episode

df_title_ep <- data.frame(Episode,Year)
colnames(df_title_ep) <- c("Number Of Episodes","Year Released") 

df_title_ep

 
list_rating <- scrape(session) %>%
  html_nodes('span.ipc-rating-star.ipc-rating-star--base.ipc-rating-star--imdb.ratingGroup--imdb-rating') %>% 
  html_text()

wholeRATING <- as.data.frame(list_rating[1:50])
colnames(wholeRATING) <- "Rating"

# Extracting Rating and Vote_Count using regular expressions
wholeRATING$Rating <- gsub("\\s*\\([^)]+\\)\\s*", "", wholeRATING$Rating)
wholeRATING$Vote_Count <- gsub(".*\\(([^)]+)\\)", "\\1", list_rating[1:50])


df_rating_vote <- wholeRATING
colnames(df_rating_vote) <- c("Rating","Vote Count") 
df_rating_vote


 
final_df <- cbind(show_df, df_rating_vote,df_title_ep )

final_df
```
 
From the 50 tv shows, select at least 5 tv shows to scrape the user reviews that will include the
reviewer’s name, date of reviewed, user rating, title of the review, and text reviews.
 
```{r}

tv_show_urls <- c(
  "https://www.imdb.com/title/tt0081846/reviews",  #COSMOS
  "https://www.imdb.com/title/tt0903747/reviews", #BREAKING BAD
  "https://www.imdb.com/title/tt0185906/reviews", # BAND OF BROTHERS
  "https://www.imdb.com/title/tt7366338/reviews", #CHERNOBYL
  "https://www.imdb.com/title/tt0417299/reviews" #Avatar: The Last Airbender
)

all_reviews <- list()

for (url in tv_show_urls) {
  # Read HTML content
  page <- read_html(url)
  
  reviewers_name <- page %>% html_nodes(".display-name-link") %>% html_text()
  dates <- page %>% html_nodes("span.review-date") %>% html_text()
  user_ratings <- page %>% html_nodes("span.rating-other-user-rating") %>% html_text()
  text_reviews <- page %>% html_nodes("div.text") %>% html_text()
  
  # Create a data frame
  reviews_df <- data.frame(
    Reviewer_Name = reviewers_name[1:5],
    Date = dates[1:5],
    User_Rating = user_ratings[1:5],
    Text_Review = text_reviews[1:5],
    stringsAsFactors = FALSE
  )
  
   all_reviews[[url]] <- reviews_df
}

final_reviews_df <- do.call(rbind, all_reviews)
colnames(final_reviews_df) <- c("Name", "Date of Review", "User Rating", "Text Reviews")

rownames(final_reviews_df) <- NULL

final_reviews_df
```

 